Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
huh, how did that happen
text

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
%exacerbated by specific artefacts,  
the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task. 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.

Although there is a vast literature on validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on stability %, working typically on continuous domains
\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
Reachability tools are
also used when discretizing the state-space for verification and
parametric synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller and the hybrid elements that relate them.  
Due to the complexity of such systems, in this particular work we focus
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic) and perform synthesis of safe digital controllers.

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system whilst remaining safe given a 
pre-selected time horizon; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

\textit{Contributions}. We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
safety properties over the state space. 
In an alternative approach, we use a verification engine based 
on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
increase the speed of the synthesis algorithm.
In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
for the safety specification.

@@

Asymptotic stability boils down to Lyapunov stability 
and convergence to an equilibrium point~\cite{Astrom08}. 
Lyapunov stability requires that model trajectories remain in 
a neighborhood of the equilibrium point. 
In the case of closed-loop LTI models as in~\eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), 
or an offset thereof. Here, we consider systems with a zero reference signal.

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable 
\textit{iff} all the roots of the characteristic polynomial 
(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
values are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ 
in terms of a check known as Jury's criterion~\cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries 
of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the 
Appendix~\ref{sec:appendix-stability}.

@@

In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
This means that the states will always be within the $n$-dimensional hyper-box. 
%, which is typically defined by the safety specification.

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$, 
which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
This means that the control input saturates in view of physical constraints.

@@

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
The second is the quantization error introduced by the digital controller, 
which 
performs operations in the domain of fixed-point numbers. 
In this section we formally outline the errors introduced by fixed-point representation of numbers.

@@

We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model. Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Solution generalisation} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Given the large solution space to be searched during the inductive
synthesis phase, we parametrize the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesize a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesize a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e., a solution in the original search space).

As well as giving us an automatic search procedure, this
parametrisation greatly increases the efficiency of our system since
languages low down the lattice are very easy to decide safety for
(i.e., the validation oracle finds an answer fast). If a program can be
synthesized in a low-complexity language, the whole procedure finishes
much faster than if synthesis had been attempted in a high-complexity
language.

@@

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesize 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k{>}\overline{k}$
(i.e., it is sufficient to unwind the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

%\todo{please eventually itemize next}
\begin{enumerate}
\item The inductive synthesis phase (i.e., {\sc synthesize}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
To synthesize a controller that satisfies the stability criteria, we require that
a computed characteristic polynomial satisifies Jury's criteria. The details of this
calculation can be found in the Appendix.

Regarding the latter, we synthesize a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
After unwinding the transition system corresponding to the previously synthesized controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

@@

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesise a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_{init}$ over time,
$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&A_t^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} A_t^i B_{n}(\nu_1+\nu_2+\nu_3) 
\end{align}
\todo{explain $B_n$ and $A_t$}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A}_t X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}_t=\bigcup_{k=1}^\infty A_t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^kA_t^iB_{n}$ are abstract matrices for the closed-loop system,
% in \eqref{eq:observer_LTI_cf} 
%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
whereas the set N is non-deterministically chosen.

>>>>

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas as in 
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
%exacerbated by specific artefacts,  
the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
by Analogue-to-Digital (A/D) \todo{later ADC and DAC} and Digital-to-Analogue (D/A) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task,  
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.
%Whilst there is a vast literature on validation of control systems,
%the subject of control synthesis has been somewhat restricted in the properties it explores.  
%Traditionally, this focuses mainly on stability %, working typically on continuous domains
particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
%\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
%models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
Beyond stability, 
recently reachability tools have been developed [cite SPACEx, Phaver, and others], 
however they have not been employed towards control synthesis. 
\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
% when discretising the state-space for verification and
%parameter synthesis~\cite{cimatti2013parameter}.

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller, 
as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), %\addtodo{[clarify next] with known configurations} 
and perform %parametric 
synthesis of safe digital controllers - the extension to more general quantitative properties is left to future work.

We describe and evaluate two approaches for synthesising digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
to unfold the dynamics forward, instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. 
\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
We provide experimental results 
showing that both approaches are able to efficiently synthesise stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

\textit{Contributions}. We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
safety properties over the state space. In an alternative approach, we use a verification engine based 
on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
the transition system necessarily for the first approach. In both approaches, we project
the maximum effect of the noise over an unbounded time and uses it as a buffer region 
for the safety specification.

@@

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
We express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.

@@

As mentioned earlier, 
in this work we are not bound to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.

In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
This means that the states will always be within the $n$-dimensional hyper-box. 
%, which is typically defined by the safety specification.

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$, 
which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
In practice, 
this means that the control input saturates in view of physical constraints.

@@

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
The second is the quantization error introduced by the digital controller, 
which 
performs operations in the domain of fixed-point numbers. 
In this section we formally outline the errors introduced by fixed-point representation of numbers.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\subsection{Fixed word length effects on matrix multiplications}
%\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model. Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Solution generalisation} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Given the large solution space to be searched during the inductive
synthesis phase, we parametrize the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesize a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesize a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e. a solution in the original search space).

As well as giving us an automatic search procedure, this
parametrisation greatly increases the efficiency of our system since
languages low down the lattice are very easy to decide safety for
(i.e. the validation oracle finds an answer fast). If a program can be
synthesized in a low-complexity language, the whole procedure finishes
much faster than if synthesis had been attempted in a high-complexity
language.

@@

%% The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
%% and generalize over continuous sets into an unbounded time, 
%% the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.

%% \addtodo{Can we come up with some sort of figure that makes it easier to visualise
%% the generalisation step in each approach?}

% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
% specialise the general CEGIS approach in order to perform solution generalisation.

@@

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach, we verify and synthesize 
a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
for this controller, and verify the controller correctness to $\overline{k}$ time steps.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k{>}\overline{k}$
(i.e. it is sufficient to unwind the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

@@

%\todo{please eventually itemize next}
\begin{enumerate}
\item The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
To synthesize a controller that satisfies the stability criteria, we require that
a computed characteristic polynomial satisifies Jury's criteria. The details of this
calculation can be found in the Appendix.

%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesize a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
%The safety criteria here must be valid for all possible allowed initial states, and so we
After unwinding the transition system corresponding to the previously synthesized controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

%\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
%\missingfigure{picture for completeness threshold}

@@

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesise a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_{init}$ over time,
$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&A_t^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} A_t^i B_{n}(\nu_1+\nu_2+\nu_3) 
\end{align}
\todo{explain $B_n$ and $A_t$}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e. the set of all reachable states at all times given an initial set $\phi_{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A}_t X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}_t=\bigcup_{k=1}^\infty A_t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^kA_t^iB_{n}$ are abstract matrices for the closed-loop system,
% in \eqref{eq:observer_LTI_cf} 
%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
whereas the set N is non-deterministically chosen.
